Twists of supersymmetric gauge theories

### 2019-08-14 paper.tex
Continuing edits to SYM section, and to dimensional reduction section

\begin{proof}
 \chris{Proof idea: start with an equivariant action functional $\mf S$ in $n$-dimensions.  There is a cochain map $C^\bullet_{\mr{loc}}(\mf L) \to C^\bullet_{\mr{loc}}(\mf L')$ by restriction.  There is a graded linear map $C^\bullet_{\mr{Lie}(\mf A) \to C^\bullet_{\mr{Lie}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.  However these two maps do, together, define a cochain map
 \[F \colon (C^\bullet_{\mr{Lie}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
 on the subcomplex consisting of those functionals where, upon restriction

 We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S) = \mf S'$ in $m$-dimensions, i.e a supersymmetric action functional.
 }
\end{proof}

>>>>

\begin{proof}
 \chris{Proof idea: start with a Poincar\'e invariant action functional $\mf S_{\mr{Poin}}$ in $n$-dimensions.  There is a cochain map
 \[F_{\mr{Poin}} \colon (C^\bullet_{\mr{Lie}(\iso(n)) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\iso(m)) \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
 given by the inclusion of $\iso(m) \inj \iso(n)$, and the restriction of fields from $n$ to $m$-dimensions.   We'll check that this map will also be compatible with the antibracket $\{,\}$, so a Maurer Cartan element $\mf S_{\mr{Poin}}$ in $n$-dimensions induces a Maurer-Cartan element $F(\mf S_{\mr{Poin}}) = \mf S'_{\mr{Poin}}$ in $m$-dimensions, i.e a Poincar\'e invariant action functional.

 Now include supertranslations.  There is a graded linear map $C^\bullet_{\mr{Lie}(\mf A) \to C^\bullet_{\mr{Lie}(\mf A')$, but it's not a cochain map because it's not compatible with the $\Gamma$-brackets.  However these two maps do, together, define a cochain map
 \[F \colon (C^\bullet_{\mr{Lie}(\mf A) \otimes C^\bullet_{\mr{loc}}(\mf L))_{\mr{Poin}} \to (C^\bullet_{\mr{Lie}(\mf A') \otimes C^\bullet_{\mr{loc}}(\mf L'))_{\mr{Poin}},\]
 on the subcomplex consisting of those functionals where, upon restriction

 }
\end{proof}
